Nanophotonic Computational Design

### 2013-02-23 defense/pres3.tex
Starting on final pres.

\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\newcommand{\nextpage}{\vfill\newpage}
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}
\newcommand{\myfig}[2]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=#2cm]{fig/#1.jpg}}
    \end{figure}
}

@@

\begin{document}
\setlength{\parskip}{0cm}
\maketitle

@@

\I  On-chip optical components are currently designed
    by tuning a small number of design parameters
\smallfig{integrated_circuit}
\pause
\I  What happens when we use the \emph{full} parameter space
    for nanophotonic design?
\nextpage

\I  The full parameter space is \emph{vast}
\smallfig{des_complexity}
\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
    \BI A virtually uncountable number 
    \I  Can only be leveraged computationally \EI
\nextpage

\smallfig{takeaway}
\I  Our work: Software to design 3D linear nanophotonic devices using 
    the full available parameter space \pause
\I  Many of these devices are
    \BI Completely novel (no previously known designs)
    \I  Extremely compact (footprints of a few vacuum wavelengths)
    \I  High efficiency ($>80\%$ transmission) \EI
\nextpage

\I  Developed by
    \BI applying (convex) optimization techniques (math)
    \I  to the area of nanophotonics (physics)
    \I  and implementing in software (programming) \EI
\pause
\I  Physics Advisory: 
    \begin{quote}CONTAINS INVOLVED MATHEMATICAL CONTENT\end{quote}
\pause
\I  Math Advisory: 
    \begin{quote}CONTAINS INVOLVED NANOPHOTONIC CONTENT\end{quote}
\nextpage

>>>>

\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\newcommand{\nextpage}{\vfill\newpage}

\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

\newcommand{\smalltitle}[1]{
    \begin{center}{\large #1}\end{center}
}

\newcommand{\myfig}[2]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=#2cm]{fig/#1.jpg}}
    \end{figure}
}

@@

\begin{document}
\setlength{\parskip}{0cm}
\maketitle
\begin{itemize} \itemsep -1pt
\I  Introduction
\I  Summary
\I  Incremental results
\I  Final result
\EI

@@

\I  On-chip optical components are currently designed
    by tuning a small number of design parameters
\smallfig{integrated_circuit}
\pause
\I  Our idea: Design using \emph{all} available parameters
    \BI If successful, full-parameter design \emph{guarantees} better devices 
    \I  i.e. We can do better by using \emph{all} the design parameters \EI

% \I  The full parameter space for nanophotonic design is \emph{vast}
% \I  How big is the full design space for nanophotonic devices?
\I The number of available design parameters for nanophotonic devices
    is \emph{enormous}
\smallfig{des_complexity}
\pause
\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
    \BI $2^{225} = 67$-digit number, uncountable \EI
\pause
\I  Realization: Hand-tuning won't work for full-parameter design
\nextpage

\I  Full-parameter design must be \emph{design-by-description}
\pause
\begin{verbatim}
\\ Human describe here.
device mux2 
    in: {freq1, freq2}
    out1 <= freq1
    out2 <= freq2
\end{verbatim}
\pause
\smallfig{thesolution}
\nextpage

\I  Realization: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description will allow us to design \emph{everything} 
    \EI
\pause
\I  Assumes that design-by-description can actually be made to work
\pause
\I  Our goal: Make it work

\oursection{Summary}
\smallfig{takeaway}
\I  Our work: Software to design 3D linear nanophotonic devices using 
    the full available parameter space \pause
\nextpage

\I  Many of these devices are
    \BI Completely novel (no previously known designs)
    \I  Extremely compact (footprints of a few vacuum wavelengths)
    \I  High efficiency ($>80\%$ transmission) \EI
\pause

\I  Developed by
    \BI applying (convex) optimization techniques (math)
    \I  to the area of nanophotonics (physics)
    \I  and implementing in software (programming) \EI
\pause

\I  Physics Advisory: 
    \begin{quote}CONTAINS INVOLVED MATHEMATICAL CONTENT\end{quote}
\nextpage
